\cvsection{Experience}
\begin{cventries}
  \cventry
    {Teaching assistant}
    {Universit\'e de Montr\'eal}
    {Montr\'eal, Qc, Canada}
    {Jan. 2017 - Apr. 2017}
    {
      \begin{cvitems}
        \item {TA for the special relativity course (PHY1652).}
        \item {Helped undergraduate students with their homework and exercices.}
      \end{cvitems}
    }
  \cventry
    {Research assistant}
    {Astrophysics Research Center of Quebec}
    {Montr\'eal, Qc, Canada}
    {May 2016 - Aug. 2016}
    {
      \begin{cvitems}
        \item {Worked under the supervision of Prof. Pierre Bergeron.}
        \item {Received an Undergraduate Student Research Award (USRA) from the NSERC for excellent academic record.}
        \item {Made a statically unbiased census of white dwarf stars within a radius of 40pc of the Sun and analyzed their physical proprieties.}
        \item {Had multiple telescopic observation nights at the Mont-M\'egantic Observatory (OMM).}
      \end{cvitems}
    }
  \cventry
    {Guide}
    {Arbraska Lafl\`eche}
    {Val-des-Monts, Qc, Canada}
    {June 2014 - Aug. 2014}
    {
      \begin{cvitems}
        \item{Was responsible for the security of the customers in the park.}
        \item{Had to entertain and deal with the customer directly to make sure his experience was satisfying.}
     \end{cvitems}
    }
  \cventry
    {Line Cook}
    {Caf\'e Soup'Herbe}
    {Chelsea, Qc, Canada}
    {June 2013 - Oct. 2013}
    {
      \begin{cvitems}
        \item{Had to cook and prepare various vegetarian dishes.}
        \item{Had to keep the freezer and the workstations clean and organized.}
      \end{cvitems}
    }

\end{cventries}
